Results

### 2018-07-17 01_clean-data.Rmd
Add session info
Nicer session info
Stop using file.path(here(.))

@@

# Load data
# results_file <- file.path(here(), "data", "test_data.csv")
results_file <- file.path(here(), "private", 
                          "NGO Crackdowns and Philanthropy, March 2018 pilot_March 23, 2018_20.01.csv")

@@

# Confirmation codes to exclude. These are people who failed the attention
# checks or who took the survey outside of MTurk.
#
# The code for determining these is in a script that is excluded from the main
# repository because of privacy issues (it deals directly with MTurk worker
# IDs), called "private/approve_mturkers.R". It outputs this text list of codes.
codes_to_exclude <- read_csv(file.path(here(), "data", "codes_to_exclude.csv"))

@@

# Save final clean data
saveRDS(results, file.path(here(), "data", "results_clean.rds"))
write_csvy(results, file = file.path(here(), "data", "results_clean.csv"),
           metadata = file.path(here(), "data", "results_clean.yaml"), na = "NA")
```

@@

saveRDS(completed_summary, file.path(here(), "data", "completion_summary.rds"))
write_csv(completed_summary, file.path(here(), "data", "completion_summary.csv"))
```

>>>>

# Load and clean data

@@

# Load data
# results_file <- file.path(here(), "data", "test_data.csv")
results_file <- here("private", 
                     "NGO Crackdowns and Philanthropy, March 2018 pilot_March 23, 2018_20.01.csv")

@@

# Confirmation codes to exclude. These are people who failed the attention
# checks or who took the survey outside of MTurk.
#
# The code for determining these is in a script that is excluded from the main
# repository because of privacy issues (it deals directly with MTurk worker
# IDs), called "private/approve_mturkers.R". It outputs this text list of codes.
codes_to_exclude <- read_csv(here("data", "codes_to_exclude.csv"))

@@

# Save final clean data
saveRDS(results, here("data", "results_clean.rds"))
write_csvy(results, file = here("data", "results_clean.csv"),
           metadata = here("data", "results_clean.yaml"), na = "NA")
```

@@

saveRDS(completed_summary, here("data", "completion_summary.rds"))
write_csv(completed_summary, here("data", "completion_summary.csv"))
```

# Original computing environment

<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>

<div id="sessioninfo" class="collapse">

```{r show-session-info, echo=TRUE}
writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))

devtools::session_info()
```

</div>

### 2018-07-17 02_analysis.Rmd
Stop using file.path(here(.))

source(file.path(here(), "lib", "graphics.R"))
source(file.path(here(), "lib", "pander_options.R"))
source(file.path(here(), "lib", "modeling.R"))

# Load data
results <- readRDS(file.path(here(), "data", "results_clean.rds"))
# qwraps2::lazyload_cache_dir("02_analysis_cache/html")

@@

  ggsave(fig_bar, filename = file.path(here(), "output", "figures", "summary-table",
                                       paste0(file_name, ".pdf")), 
         width = 1, height = 0.2, device = cairo_pdf)
  ggsave(fig_bar, filename = file.path(here(), "output", "figures", "summary-table",
                                       paste0(file_name, ".png")), 
         width = 1, height = 0.2, type = "cairo", bg = "transparent", dpi = 300)

@@

  ggsave(fig_hist, filename = file.path(here(), "output", "figures", "summary-table",
                                        paste0(file_name, ".pdf")), 
         width = 1, height = 0.2, device = cairo_pdf)
  ggsave(fig_hist, filename = file.path(here(), "output", "figures", "summary-table",
                                        paste0(file_name, ".png")), 
         width = 1, height = 0.2, type = "cairo", bg = "transparent", dpi = 300)

@@

```{r check-conditions, results="asis"}
results %>% count(crackdown, issue, funding) %>% 
  rename(Crackdown = crackdown, Issue = issue, Funding = funding) %>% 
  janitor::adorn_totals(., where = "row") %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Balance of experimental conditions {#tbl:experimental-conditions}") %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-experimental-conditions.md"))
```

@@

results_summary_stats %>% 
  select(-N) %>% 
  pandoc.table.return(caption = "Descriptive statistics {#tbl:descriptive-stats}",
                      split.cell = 80, split.table = Inf) %T>% 
  cat(file = file.path(here(), "output", "tables", "tbl-descriptive-stats.md")) %>% 
  cat()
```

@@

conditions_summary_clean %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Average likelihood and amount donated across experimental conditions {#tbl:avg-results}") %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-avg-results.md"))
```

@@

plot_donate_summary %T>% 
  print() %T>%
  ggsave(., filename = file.path(here(), "output", "figures", "donate_summary.pdf"),
         width = 9, height = 4, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "donate_summary.png"),
         width = 9, height = 4, units = "in", type = "cairo", dpi = 300)
```

@@

plot_amount_summary %T>% 
  print() %T>%
  ggsave(., filename = file.path(here(), "output", "figures", "amount_summary.pdf"),
         width = 9, height = 2.75, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount_summary.png"),
         width = 9, height = 2.75, units = "in", type = "cairo", dpi = 300)
```

@@

conditions_summary_clean %>% 
  select(1:3) %>% 
  slice(-n()) %>% 
  bind_cols(interpretation) %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Combinations of coefficients to add to determine means across experimental conditions {#tbl:coefficients-to-add}") %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-coefficients-to-add.md"))
```

@@

huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
       coefs = clean_coefs_named[clean_coefs_named %in% coefs_to_include],
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-models-amount.md"))
```

@@

plot_amount_singles %T>%
  print() %T>%
  ggsave(., filename = file.path(here(), "output", "figures", "amount_single_summary.pdf"),
         width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount_single_summary.png"),
         width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

@@

(plot_amount_all + 
    plot_annotation(caption = "90% credible intervals shown around each point",
                    tag_levels = "A", theme = theme_ngos())) %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-medians.pdf"),
         width = 8, height = 4.25, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-medians.png"),
         width = 8, height = 4.25, units = "in", type = "cairo", dpi = 300)
```

@@

plot_diffs_singles %T>%
  print() %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-singles-diffs.pdf"),
         width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-singles-diffs.png"),
         width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-single-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_i,
          diffs_coef_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions {#tbl:amount-single-diffs}") %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-amount-single-diffs.md"))
```

@@

(plot_diffs_all +
  plot_annotation(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
                  tag_levels = "A", theme = theme_ngos())) %T>%
  ggsave(., filename = file.path(here(), "output", "figures", "amount-diffs.pdf"),
         width = 8, height = 5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = file.path(here(), "output", "figures", "amount-diffs.png"),
         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-all-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_ci,
          diffs_coef_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `Crackdown - No crackdown~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between amounts donated in "crackdown" (treatment) and "no crackdown" (control) conditions {#tbl:amount-diffs}') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-amount-diffs.md"))
```

@@

huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
       coefs = clean_coefs_named[clean_coefs_named %in% coefs_to_include],
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-models-likelihood.md"))
```

@@

(plot_likely_all +
  plot_annotation(caption = "90% credible intervals shown around each point",
                  tag_levels = "A", theme = theme_ngos())) %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-medians.pdf"),
         width = 8, height = 4.25, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-medians.png"),
         width = 8, height = 4.25, units = "in", type = "cairo", dpi = 300)
```

@@

plot_diffs_likely_singles %T>%
  print() %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-singles-diffs.pdf"),
         width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-singles-diffs.png"),
         width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-single-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_i,
          diffs_coef_likely_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions {#tbl:likelihood-single-diffs}") %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-single-diffs.md"))
```

@@

(plot_diffs_likely_all +
    plot_annotation(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
                    tag_levels = "A", theme = theme_ngos())) %T>%
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-diffs.pdf"),
         width = 8, height = 5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-diffs.png"),
         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-all-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_ci,
          diffs_coef_likely_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `Crackdown - No crackdown~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between likelihood to donate in "crackdown" (treatment) and "crackdown" (control) conditions {#tbl:likelihood-diffs}') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-diffs.md"))
```

@@

hypotheses %>% 
  pandoc.table.return(justify = "ll", style = "grid", keep.line.breaks = TRUE,
                      caption = "Summary of all hypotheses {#tbl:hypotheses}") %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-hypotheses.md"))
```

>>>>

source(here("lib", "graphics.R"))
source(here("lib", "pander_options.R"))
source(here("lib", "modeling.R"))

# Load data
results <- readRDS(here("data", "results_clean.rds"))
# qwraps2::lazyload_cache_dir("02_analysis_cache/html")

@@

  ggsave(fig_bar, filename = here("output", "figures", "summary-table",
                                  paste0(file_name, ".pdf")), 
         width = 1, height = 0.2, device = cairo_pdf)
  ggsave(fig_bar, filename = here("output", "figures", "summary-table",
                                  paste0(file_name, ".png")), 
         width = 1, height = 0.2, type = "cairo", bg = "transparent", dpi = 300)

@@

  ggsave(fig_hist, filename = here("output", "figures", "summary-table",
                                   paste0(file_name, ".pdf")), 
         width = 1, height = 0.2, device = cairo_pdf)
  ggsave(fig_hist, filename = here("output", "figures", "summary-table",
                                   paste0(file_name, ".png")), 
         width = 1, height = 0.2, type = "cairo", bg = "transparent", dpi = 300)

@@

```{r check-conditions, results="asis"}
results %>% count(crackdown, issue, funding) %>% 
  rename(Crackdown = crackdown, Issue = issue, Funding = funding) %>% 
  janitor::adorn_totals(., where = "row") %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Balance of experimental conditions {#tbl:experimental-conditions}") %>% 
  cat(file = here("output", "tables", "tbl-experimental-conditions.md"))
```

@@

results_summary_stats %>% 
  select(-N) %>% 
  pandoc.table.return(caption = "Descriptive statistics {#tbl:descriptive-stats}",
                      split.cell = 80, split.table = Inf) %T>% 
  cat(file = here("output", "tables", "tbl-descriptive-stats.md")) %>%
  cat()
```

@@

conditions_summary_clean %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Average likelihood and amount donated across experimental conditions {#tbl:avg-results}") %>% 
  cat(file = here("output", "tables", "tbl-avg-results.md"))
```

@@

plot_donate_summary %T>% 
  print() %T>%
  ggsave(., filename = here("output", "figures", "donate_summary.pdf"),
         width = 9, height = 4, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "donate_summary.png"),
         width = 9, height = 4, units = "in", type = "cairo", dpi = 300)
```

@@

plot_amount_summary %T>% 
  print() %T>%
  ggsave(., filename = here("output", "figures", "amount_summary.pdf"),
         width = 9, height = 2.75, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "amount_summary.png"),
         width = 9, height = 2.75, units = "in", type = "cairo", dpi = 300)
```

@@

conditions_summary_clean %>% 
  select(1:3) %>% 
  slice(-n()) %>% 
  bind_cols(interpretation) %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Combinations of coefficients to add to determine means across experimental conditions {#tbl:coefficients-to-add}") %>% 
  cat(file = here("output", "tables", "tbl-coefficients-to-add.md"))
```

@@

huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
       coefs = clean_coefs_named[clean_coefs_named %in% coefs_to_include],
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = here("output", "tables", "tbl-models-amount.md"))
```

@@

plot_amount_singles %T>%
  print() %T>%
  ggsave(., filename = here("output", "figures", "amount_single_summary.pdf"),
         width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "amount_single_summary.png"),
         width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

@@

(plot_amount_all + 
    plot_annotation(caption = "90% credible intervals shown around each point",
                    tag_levels = "A", theme = theme_ngos())) %T>% 
  ggsave(., filename = here("output", "figures", "amount-medians.pdf"),
         width = 8, height = 4.25, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "amount-medians.png"),
         width = 8, height = 4.25, units = "in", type = "cairo", dpi = 300)
```

@@

plot_diffs_singles %T>%
  print() %T>% 
  ggsave(., filename = here("output", "figures", "amount-singles-diffs.pdf"),
         width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "amount-singles-diffs.png"),
         width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-single-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_i,
          diffs_coef_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions {#tbl:amount-single-diffs}") %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-amount-single-diffs.md"))
```

@@

(plot_diffs_all +
  plot_annotation(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
                  tag_levels = "A", theme = theme_ngos())) %T>%
  ggsave(., filename = here("output", "figures", "amount-diffs.pdf"),
         width = 8, height = 5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("output", "figures", "amount-diffs.png"),
         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-all-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_ci,
          diffs_coef_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `Crackdown - No crackdown~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between amounts donated in "crackdown" (treatment) and "no crackdown" (control) conditions {#tbl:amount-diffs}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-amount-diffs.md"))
```

@@

huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
       coefs = clean_coefs_named[clean_coefs_named %in% coefs_to_include],
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = here("output", "tables", "tbl-models-likelihood.md"))
```

@@

(plot_likely_all +
  plot_annotation(caption = "90% credible intervals shown around each point",
                  tag_levels = "A", theme = theme_ngos())) %T>% 
  ggsave(., filename = here("output", "figures", "likelihood-medians.pdf"),
         width = 8, height = 4.25, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "likelihood-medians.png"),
         width = 8, height = 4.25, units = "in", type = "cairo", dpi = 300)
```

@@

plot_diffs_likely_singles %T>%
  print() %T>% 
  ggsave(., filename = here("output", "figures", "likelihood-singles-diffs.pdf"),
         width = 7, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "likelihood-singles-diffs.png"),
         width = 7, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-single-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_i,
          diffs_coef_likely_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions {#tbl:likelihood-single-diffs}") %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likelihood-single-diffs.md"))
```

@@

(plot_diffs_likely_all +
    plot_annotation(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0",
                    tag_levels = "A", theme = theme_ngos())) %T>%
  ggsave(., filename = here("output", "figures", "likelihood-diffs.pdf"),
         width = 8, height = 5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("output", "figures", "likelihood-diffs.png"),
         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-all-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_ci,
          diffs_coef_likely_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `Crackdown - No crackdown~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between likelihood to donate in "crackdown" (treatment) and "crackdown" (control) conditions {#tbl:likelihood-diffs}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likelihood-diffs.md"))
```

@@

hypotheses %>% 
  pandoc.table.return(justify = "ll", style = "grid", keep.line.breaks = TRUE,
                      caption = "Summary of all hypotheses {#tbl:hypotheses}") %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-hypotheses.md"))
```
